Something something values disclosure replication

### 2022-07-11 paper/paper.Qmd
working on wide table problem for PDF output

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
toc: true
execute:
    echo: false
bibliography: |
  transparency-Hicks.yaml
---

@@

library(here)
here()
out_dir = here('out')
```

@@

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS(here(out_dir, '03_bc_tbl.Rds'))
bc_tbl
```

@@

```{r}
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
shared_values_tbl = readRDS(here(out_dir, '03_shared_values_tbl.Rds'))
shared_values_tbl
```

@@

```{r}
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5-consumer, interaction between participant values and consumer risk sensitivity"
readRDS(here(out_dir, '03_eb_tbl.Rds'))
```

@@

```{r}
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5-transparency, interaction between participant values and transparency penalty"
readRDS(here(out_dir, '03_ec_tbl.Rds'))
```

@@

```{r}
#| label: tbl-sci-part
#| tbl-cap: "Regression analysis of interaction between scientist values and participant values"
readRDS(here(out_dir, '03_sci_part_tbl.Rds'))
```

>>>>

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
toc: true
execute:
    echo: false
bibliography: |
  transparency-Hicks.yaml
header-includes:
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\landscape}
  - \newcommand{\elandscape}{\endlandscape}
  # - \usepackage{endfloat}
---

@@

library(gtsummary)
library(here)
here()
out_dir = here('out')
```

```{r}
#| label: tbl-test
#| tbl-cap: "Testing"
knitr::include_graphics('../out/03_eb_tbl.pdf')
```

@tbl-test

<!-- \blandscape -->
```{r}
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
readRDS(here(out_dir, '03_shared_values_tbl.Rds')) |> 
    as_hux_table() |> 
    huxtable::set_width(1)
```
<!-- \elandscape -->

@@

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
readRDS(here(out_dir, '03_bc_tbl.Rds')) |> 
    as_hux_table()
```

@@

<!-- \blandscape -->

```{r}
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
readRDS(here(out_dir, '03_shared_values_tbl.Rds')) |> 
    as_hux_table()
```
<!-- \elandscape -->

@@

```{r}
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5-consumer, interaction between participant values and consumer risk sensitivity"
readRDS(here(out_dir, '03_eb_tbl.Rds')) |> 
    as_hux_table()
```

@@

```{r}
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5-transparency, interaction between participant values and transparency penalty"
readRDS(here(out_dir, '03_ec_tbl.Rds')) |> 
    as_hux_table()
```

@@

```{r}
#| label: tbl-sci-part
#| tbl-cap: "Regression analysis of interaction between scientist values and participant values"
readRDS(here(out_dir, '03_sci_part_tbl.Rds')) |> 
    as_hux_table()
```
